---
drake_cache: ".dependency"
---

## Setup environment

  * Addins: Initiate drake -> `drake$source_plan()` -> `drake$makePlan()`.
  
  * `web$browse()` to see the output. 
  
  * If any change to Rmd or js/ and css/ folder, then `web$update()` -> `web$browse()` to see the change.
  
  * Your html output file is in `web$output_filepath()`.

```{r makecondition}
library(dplyr)
library(htmltools)
library(econR)
.GlobalEnv$web <- econR::Web()
web$foldername="docs2" # output folder name
web$html_filename <- "index.html"

```



## Dependency

### External resource

```{r dep_external}
dep_external <-
  htmltools::htmlDependency(
    name = "materialise",
    version = "1.0.0",
    src = c(
      href="https://cdnjs.cloudflare.com/ajax/libs/materialize/1.0.0/"
    ),
    stylesheet = c(
      "css/materialize.min.css"
    ),
    script = c(
      "js/materialize.min.js"
    )
  )
```

### Internal resource

```{r dep_local}
.root <- rprojroot::is_rstudio_project$make_fix_file()
dep_local <- htmltools::htmlDependency(
  name = "assets",
  version = "1.0.0",
  src = c(
    filepath = file.path(.root())
  ),
  stylesheet = c(
    "css/"
  ),
  script = c(
    "js/"
  ),
  attachment = c(
    "img/"
  ),
  all_files = T
)
```

So when needed:
```{r img_bart}
dep_path <- econR::htmlDependency_path(dep_local)
img_bart <- tags$img(
  src=file.path(
    dep_path$attachment$img,
    "bart.png")
)
```


## Materialise Framework

  * <https://materializecss.github.io/materialize/>

## Body Tags

```{r bodyTags}
bodyTags <- {
  htmltools::tagList(
    tags$div(class="container",
             tags$div(class="row",
                      tags$div(class="col s12",
                               img_bart)
                      ))
  )
}
```


## HTML Structure

```{r html_placeholder}
html_placeholder <- tags$html(
  tags$head(
    do.call(htmltools::tagList, headTags),
    tags$meta(
      name="viewport",
      content="width=device-width, initial-scale=1.0"
    )
  ),
  tags$body(
    do.call(htmltools::tagList, bodyTags)
  )
)
```

## Dependencies

### Head Tags

```{r headTags}
headTags <- {
  htmltools::tagList(
    htmltools::tags$link(
      href="https://fonts.googleapis.com/icon?family=Material+Icons",
      rel="stylesheet"
    )
  )
}
```

### Define dependency

```{r myDependency}
myDependency <- htmltools::htmlDependency(
  name="myown",
  version="1.0",
  src=c(filepath=web$cssJsPath),
  stylesheet = "css/mystyle.css",
  script = "js/mydesign.js",
  head = '<link rel="stylesheet" href="https://fonts.googleapis.com/css?family=Noto+Sans+TC">
'
)
```

  * If src is in other path, use `web$config_cssJsPath("your_path")` in **makecondition** -- no need to change `web$cssJsPath` (it will change accordingly).


```{r local_jquery}
local_jquery <- 
  htmltools::htmlDependency(
    name="jquery",
    version="3.5.1",
    src=c(href = "lib/jquery-3.5.1"),
    # to use the same library here must use href, not filepath; otherwise, the current jquery system will be removed.
    script = c("jquery.min.js")
  )
```

### Attach dependency


```{r html_complete}
html_complete <- 
  htmltools::tagList(
    html_placeholder,
    web$htmlDependencies$materialise(),
    local_jquery, 
    myDependency,
    dep_local,
    dep_external
  )
```

  * If not using jquery from htmlwidgets, replace `local_jquery` with `web$htmlDependencies$jquery()`


## Save

```{r save_html}
htmltools::save_html(
  html_complete, 
  file = web$output_filepath(),
  libdir="lib"
)
```

## Browse

```{r}
web$browse()
```





## JS


<!--JS end-->
