---
drake_cache: ".sheets"
---

  * <https://developers.google.com/sheets/api/quickstart/js>
  
```{r}
browseURL("https://developers.google.com/sheets/api/quickstart/js")
```


```{r makecondition}
library(dplyr)
library(htmltools)
library(econR)
.root <- rprojroot::is_rstudio_project$make_fix_file()
.GlobalEnv$web <- econR::Web()
web$foldername="docs" # output folder name
web$html_filename <- "sheet_quickstart.html"

```

## Google Sheet

### Dependency: Internal


```{r googleSheets}
googleSheets <- list()
googleSheets$dependency <-
    htmltools::htmlDependency(
      name="google_sheet",
      version="1.0.0",
      src = c(filepath=file.path(.root(),"js")),
      script = "googleSheets.js")
googleSheets$after_body <- 
      htmltools::HTML('<script async defer src="https://apis.google.com/js/api.js"
      onload="this.onload=function(){};handleClientLoad()"
      onreadystatechange="if (this.readyState === \'complete\') this.onload()">
    </script>
')

googleSheets
```

### Button


```{r signInBtn}
tagList(
  tags$p(" Google Sheets API Quickstart"),
    #--Add buttons to initiate auth sequence and sign out--, 
  tags$button(id="authorize_button", style="display: none;"," Authorize"),
  tags$button(id="signout_button", style="display: none;"," Sign Out"),
  tags$pre(id="content", style="white-space: pre-wrap;"," ")
)
   
```

### Dependency


## Body Tags

```{r bodyTags}
bodyTags <- {
  htmltools::tagList(
    tags$main(
      tags$h5(class="center-align",
      "Google sheets quickstart")
    ),
    tags$div(class="container",
             tags$div(class="row",
                      tags$div(class="col s12",
                               signInBtn)
                      )),
    googleSheets$after_body
  )
}
```


## HTML Structure

```{r html_placeholder}
html_placeholder <- tagList(
  tags$head(
    do.call(htmltools::tagList, headTags)
  ),
  tags$body(
    do.call(htmltools::tagList, bodyTags)
  )
)
```

## Dependencies

### Head Tags

```{r headTags}
headTags <- {
  htmltools::tagList(
    htmltools::tags$link(
      href="https://fonts.googleapis.com/icon?family=Material+Icons",
      rel="stylesheet"
    ),
    tags$meta(
      name="viewport",
      content="width=device-width, initial-scale=1.0"
    )
  )
}
```

### Define dependency

  * If src is in other path, use `web$config_cssJsPath("your_path")` in **makecondition** -- no need to change `web$cssJsPath` (it will change accordingly).


```{r local_jquery}
local_jquery <- 
  htmltools::htmlDependency(
    name="jquery",
    version="3.5.1",
    src=c(href = "lib/jquery-3.5.1"),
    # to use the same library here must use href, not filepath; otherwise, the current jquery system will be removed.
    script = c("jquery.min.js")
  )
```

### Attach dependency


```{r html_complete}
html_complete <- 
  htmltools::tagList(
    html_placeholder,
    web$htmlDependencies$materialise(),
    web$htmlDependencies$jquery(), 
    googleSheets$dependency
  )
```

  * If not using jquery from htmlwidgets, replace `local_jquery` with `web$htmlDependencies$jquery()`


## Save

```{r save_html}
htmltools::save_html(
  html_complete, 
  file = web$output_filepath(),
  libdir="lib"
)
```

## Browse

```{r}
web$browse()
```





## JS


<!--JS end-->
